Thread Pool in GeckoDB/BOLSTER

### 2018-05-09 Presentations/Milestone2/presentation.tex
Begin milestone 2 presentation

\title{Scientific Team Project}
\subtitle{Thread Pool in GeckoDB/BOLSTER}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise, Benedikt Zeilinger}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

%Topic, schedule, and team presentation & first results of literature research

@@

\section{Motivation}
	\begin{frame}
		\frametitle{Motivation}
		\begin{center}
			\includegraphics[width=0.6\textwidth]{img/bigpicture.png}
		\end{center}
	\end{frame}

\section{Introduction}
	\begin{frame}
		\frametitle{Introduction}
		\begin{itemize}
			\item \emph{In computer programming, a thread pool is a software design pattern for achieving concurrency of execution in a computer program.}
			\item Pool of Threads to distribute parallel tasks
			\item Reduces overhead of creating new threads by reusing existing threads.
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Current Situation}
		\begin{itemize}
			\item Operations are spawning dozens of threads, which are not handled and managed..
			\item Heavy overhead of creating and removing threads
			\item After some operations profiler dies (too many threads).
			\item Debugging/Profiling not possible due to number of threads 
		\end{itemize}
	\end{frame}

	\begin{frame}
		\frametitle{Desirable Situation}
		\begin{itemize}
			\item Reuse of Threads with thread pools.
			\item Reduce overhead of thread management
			\item Improve maintainability of parallel code
			\item Defy competition to existing thread pool libs
		\end{itemize}
	\end{frame}

\section{Planning}

\begin{frame}
	\frametitle{Team Responsibilities}
		\centering
		\begin{tabular}{l l} \hline
			\textbf{Team Role} & \textbf{Name} \\ \hline
			Team Leader & Johann Wagner \\
			Implementation & Johannes Wünsche \\
			Research & Robert Jendersie \\
			Time Management & Marten Wallewein-Eising \\
			Writing & Benedikt Zeilinger\\ \hline
		\end{tabular}
\end{frame}

\begin{frame}
	\frametitle{Schedule}
	\includegraphics[width=1.0\textwidth]{img/schedule.png}
\end{frame}

\section{Literature Research}
    \begin{frame}
        \frametitle{Literature Research}
        \begin{itemize}
            \item Xu, Dongping, and Brett Bode. \emph{"Performance study and dynamic optimization design for thread pool systems".} Diss. United States. Department of Energy. Office of Science, 2004.
            \item Ling, Yibei, Tracy Mullen, and Xiaola Lin. \emph{Analysis of optimal thread pool size.} ACM SIGOPS Operating Systems Review 34.2 (2000): 42-55.
            \item Kang, DongHyun, et al. \emph{Prediction-based dynamic thread pool scheme for efficient resource usage.} Computer and Information Technology Workshops, 2008. CIT Workshops 2008. IEEE 8th International Conference on. IEEE, 2008.
        \end{itemize}
    \end{frame}

>>>>

\title{Thread Pool in GeckoDB/BOLSTER}
\subtitle{Milestone II: Concept \& additional literature research}
\author{Johann Wagner, Johannes Wünsche, Marten Wallewein-Eising, Robert Jenderise, Benedikt Zeilinger}
\date{\today}
\institute{Otto von Guericke University, Magdeburg}

% Milestone II: Concept & additional literature research

@@

\section{Previously...}
\begin{frame}
	\frametitle{Previously in Thread Pool in GeckoDB/BOLSTER}
	\begin{itemize}
		\item Operations are spawning dozens of threads, which are not handled and managed
		\item Heavy overhead of creating and removing threads
		\item After some operations profiler dies (too many threads)
	\end{itemize}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{img/thumbs_down.png}
	\end{center}
\end{frame}

\begin{frame}
	\frametitle{Previously in Thread Pool in GeckoDB/BOLSTER}
	\begin{itemize}
		\item Reuse of Threads with thread pools.
		\item Reduce overhead of thread management
		\item Improve maintainability of parallel code
	\end{itemize}
	\begin{center}
		\includegraphics[width=0.3\textwidth]{img/thumbs_up.png}
	\end{center}
\end{frame}

\section{Concept and Design}
\begin{frame}
	\frametitle{Concept}
	\begin{itemize}
		\item Thread pool with runtime fixed amount of threads and lock free priority queue
		\item Tasks are not preemtable and independent
		\item Array of tasks passed to an enqueue function, which waits until all tasks are finished
		\item Threads without tasks idle until they get a new one
		\item Monitoring/managing state and assigned task of each thread
	\end{itemize}
\end{frame}

\begin{frame}
\frametitle{Design}
	\begin{center}
		\includegraphics[width=0.9\textwidth]{img/pool_queue.png}
	\end{center}
\end{frame}

\section{Current Progress}

\section{Next Steps}

\section{Additional Literature Research}
    \begin{frame}
        \frametitle{Literature Research}
        \begin{itemize}
            \item 
        \end{itemize}
    \end{frame}
